Death by Dropdown? Engineer Insightful Shiny Apps with Behavioral Science

### 2025-09-07 conference-materials/2025_posit-conf/draft.qmd
Add examples and visuals
- Introduced script/plot to highlight attention heatmap using F-pattern logic
- Added `summary-report.R` to visualize before/after dashboard metrics
- Embedded new images into HTML presentation, replacing placeholders and old visuals
- Updated QMD sections to reflect revised content structure and visual storytelling

```{r}
library(dplyr)
library(bidux)

@@

![](img/telemetry-heatmap.png)

@@

```{r}
#| echo: false

@@

```{r}
# Using production telemetry
telemetry_path <- conn_telemetry_db("dashboard_telemetry.sqlite")

@@

![](https://media.giphy.com/media/l0IykOsxLECVejOzm/giphy.gif)<br>
*Users interpreting your carefully crafted visualizations*

@@

:::: {.columns}
::: {.column width="50%"}
### Anchoring Bias
```{r}
#| eval: false

@@

::: {.column width="50%"}
### Framing Effects
```{r}
# Don't specify bias_mitigations - let {bidux} suggest them!
anticipate_stage <- bid_anticipate(
  previous_stage = notice_stage,
  # bias_mitigations = NULL,
  include_accessibility = TRUE
)
```
:::
::::

@@

![](img/confirmation-bias-toggle.png)

@@

```{r}
flags <- bid_flags(issues)
structure_stage <- bid_structure(
  previous_stage = anticipate_stage,
  telemetry_flags = flags
)
structure_stage$suggestions
```

@@

```{r}
all_suggestions <- c(
  interpret_stage$suggestions,
  notice_stage$suggestions,
  anticipate_stage$suggestions,
  structure_stage$suggestions
)
all_suggestions
```

@@

:::: {.columns}
::: {.column width="50%"}
### Before: Chaos
![](img/before-overload.png)

@@

::: {.column width="50%"}
### After: Journey
![](img/after-structured.png)

@@

::: {.fragment}
![](img/validate-summary.png)

@@

![QR for contact](img/qr-combined.png)
:::

::: {.notes}
- 1 minute close
- "No more death by dropdown!"
- "Questions?"
- Thank organizers if time
:::

## Bonus: Quick Reference Card

| Stage | Problem | Solution | {bidux} Function |
|-------|---------|----------|------------------|
| **I**nterpret | No clear question | Define destination | `bid_interpret()` |
| **N**otice | Hidden friction | Telemetry reveals | `bid_notice()` |
| **A**nticipate | Cognitive biases | Guard rails | `bid_anticipate()` |
| **S**tructure | Chaos overwhelms | Progressive disclosure | `bid_structure()` |
| **V**alidate | Unclear outcomes | Plain language | `bid_validate()` |

::: {.notes}
- Only show if someone asks for summary
- "Email me for full guide"
:::

>>>>

```{r, interpret-stg}
library(dplyr)
library(bidux)

@@

:::: {.columns}
::: {.column width="50%"}
![](img/telemetry-heatmap.png)
:::

::: {.column width="50%"}
![](img/telemetry-sessions-heatmap.png)
:::
::::

@@

```{r, telemetry-data}
#| echo: false

@@

```{r, notice-stg}
# Using production telemetry
telemetry_path <- conn_telemetry_db("dashboard_telemetry.sqlite")

@@

![](https://media.giphy.com/media/l0IykOsxLECVejOzm/giphy.gif)

*Users interpreting your carefully crafted visualizations*

@@

:::: {.columns}
::: {.column width="50%"}
### Anchoring Bias

```{r}
#| eval: false

@@

::: {.column width="50%"}
### Framing Effects

```{r}
# Don't specify bias_mitigations - let {bidux} suggest them!
anticipate_stage <- bid_anticipate(
  previous_stage = notice_stage,
  # bias_mitigations = NULL,
  include_accessibility = TRUE
)
```
:::
::::

@@

<!-- ![](img/confirmation-bias-toggle.png) -->

@@

```{r}
flags <- bid_flags(issues)

structure_stage <- bid_structure(
  previous_stage = anticipate_stage,
  telemetry_flags = flags
)

structure_stage$suggestions
```

@@

```{r}
all_suggestions <- c(
  interpret_stage$suggestions,
  notice_stage$suggestions,
  anticipate_stage$suggestions,
  structure_stage$suggestions
)

all_suggestions
```

@@

:::: {.columns}
::: {.column width="50%"}
### Before: Chaos
<!-- ![](img/before-overload.png) -->

@@

::: {.column width="50%"}
### After: Journey
<!-- ![](img/after-structured.png) -->

@@

::: {.fragment}
![](img/summary-report.png)

@@

<!-- ![QR for contact](img/qr-combined.png) -->
:::

::: {.notes}
- 1 minute close
- "No more death by dropdown!"
- "Questions?"
- Thank organizers
:::
